\ProvidesFile{ap-bugs}[2022-10-14 bugs appendix]

\makeatletter
\newcommand{\bug}[2]
  {%
    \vspace{6pt}
    \noindent
    {%
      \bfseries
      \ifthen{\equal{high}{#2}}{\color{red}}%
      \ifthen{\equal{low}{#2}}{\color{green}}%
      \ifthen{\equal{done}{#2}}{\color{black}}%
      \ifthen{\equal{fixed}{#2}}{\color{black}}%
      \ifthen{\equal{wait}{#2}}{\color{black}}%
      \ifthen{\equal{not}{#2}}{\color{gray}}%
      {\fontsize{9}{10}\reset@font\bf BUG}
      #1.
    }%
    \ignorespaces
  }
\makeatother

\chapter{BUGS}

This appendix lists all bugs/comments/issues/etc\@.
under the generic name `bug'.
Each bug is assigned a number when I learn of it.
Bug numbers are 1, 2,~\ldots~.
I started keeping track of bugs in this fashion on February 26, 2022,
and some previously known bugs are included in this list.
A color indicates a bug's priority:

\begin{tabular}{@{}ll@{}}
  \toprule
  \bf Description& \bf Color\\
  \midrule
  done or waiting on someone else& \color{black}black\\
  high priority or easy to do& \color{red}red\\
  low priority& \color{green}green\\
  not prioritized yet& \color{gray}gray\\
  \bottomrule\\
\end{tabular}

See the ap-bugs.tex file for the \LaTeXLogo\ input for this appendix.


\section{These bugs need to be looked at}

% I need to fix the following things in \PurdueThesis.
% They are listed in bug number order.

\bug{1}{high}
Table of Contents is double-spaced instead of 1\sfrac12 spacing.
{\small
  Tighten up section and less significant headings spacing?
  Reported by Anita Adams Sale on 2021-03-17.%
}

\bug{2}{high}
List of Figures indented $\approx$\sfrac14 inch
more than List of Tables.
{\small
  Reported by Anita Adams Sale on 2021-03-17.
  Still happening on 2021-11-30.
  Looked ok on 2022-08-26
  but I think this problem is probably intermittent.
  Keep Ashlee Messersmith,
  Anita Adams Sale,
  and Sherrie Tucker informed.%
}

\bug{6}{not}
APA reference style indents references too far on left.
{\small
Reported by Mark Senn on 2021-04-08.%
}

\bug{8}{not}
Use ``Last Accessed: yyyy-mm-dd.'' urldate in bibliography.
{\small
  Reported by Mark Senn on 2021-04-19.%
}

\bug{9}{low}
Check that |@{}| is before the left column
and after the right column in all tables.
{\small
  Reported by Mark Senn on 2021-04-19.%
}

\bug{11}{low}
Bibliography change:
Change,
for example,
``Acoustical Science and Technology, vol.~23, no.~1''
to
``Acoustical Science and Technology {\bfseries 23\/} ({\bfseries 1\/})''.
{\small
  Reported by Daniel Joesph Carr on 2021-06-16.%
}

\bug{12}{low}
Bibliography change:
Change,
for example,
|M.~Abramowitz and I.A.~Stegun, Eds.,|
to
|M.~Abramowitz and I.A.~Stegun, editors,|.
{\small
  Reported by Daniel Joesph Carr on 2021-06-16.
}

\bug{13}{low}
Headings containing a SmallCaps font do not work.
{\small
  Reported by Javad (Nima) Darivandpour on 2021-06-29.
  See \ref{section-headings-with-smallcaps-font}.%
}

\bug{14}{low}
On Overleaf only,
when using
|\def\ZZshowtimestamp{true}|,
the time and sometimes the date
are wrong at the top of the page.
{\small
  Reported by Mark Senn on 2022-02-25.
  This might be due to using
  |\ExplSyntaxOn| \ldots |\ExplSyntaxOff|
  and having |:| and/or other characters having the wrong catcode.
}

\bug{15}{not}
Left reference section margin is ok if a person has 10--99 references.
{\small
  Figure out how to adjusting margin for 1--9 or over 99 references.
  Reported by Mark Senn on unknown date.
}

\bug{19}{high}
|Bibliography| and |References| missing from navigation panel.
{\small
  Reported by Mark Senn on 2022-02-28.
  REFERENCES was in navigation panel on 2022-08-26.
}

\bug{20}{high}
|Bibliography| and |References| should be in all caps.
{\small
  Reported by Mark Senn on 2022-02-28.
  REFERENCES was in all caps on 2022-08-26.%
}

\bug{21}{low}
IE students should be able
to specify IEEE
or APA bibliography format.
{\small
  Reported by Patrick Brunese on 2022-03-04.%
}

\section{These bugs are waiting on a reply from someone other than Mark Senn}

\bug{10}{wait}
Using
|linktoc = section|
does not work with captions with
|\frac|.
{\small
  Reported by Mark Senn on 2021-05-27.
  In the short-term,
  check with Ashlee Messersmith
  if {\tt linktoc = page} can be used.
  If that's ok make the change
  and look into changing captions from my code
  to \LaTeXLogo's code.
  Waiting on Ashlee Messersmith.
}

\section{These bugs have been rejected or fixed}

\bug{3}{done}
Use ``Last Accessed: dd/mm/yy.'' urldate in bibliography.
{\small
  Reported by Priyank Kalgaonkar on 2021-04-06.
  Answered by Mark Senn on 2022-02-27.
  The United States uses mm/dd/yy and other countries use dd/mm/yy
  \cite{cms17-ambiguous-dates}.
  I recommend using what your bibliography style defines
  or the unambiguous ISO 8601 standard yyyy-mm-dd
  \cite{cms17-iso-dates}.%
}

\bug{4}{done}
Change citation, e.g., |[6], [71]| to |[6,71]|.
{\small
  Reported by Mark Senn on 2021-04-07.
  Fixed on 2022-04-14.
  Tested ok on 2022-04-14.%
}

\bug{5}{done}
Change citation, e.g., |[6], [7], [8]| to |[6-8]|.
{\small
  Reported by Mark Senn on 2021-04-07.
  Fixed on 2022-04-14.
  Tested ok on 2022-04-14.%
}

\bug{7}{fixed}
Non-nested description environments have bold items.
Nested description environments have non-bold items.
How come?
Are the indentations correct?
{\small
  Reported by Mark Senn on 2021-04-09.
  Tested ok on 2021-05-31.%
}

\bug{16}{fixed}
Add DTECH degree.
{\small
  Reported by Mark Senn on unknown date.
  Program ``Technology''
  and degree ``Doctor of Technology'' worked ok
  on 2022-08-26.%
}

\bug{17}{fixed}
Allow |,| (comma) in |\title|.
{\small
  Reported by Mark Senn on unknown date.
  Tested ok on 2021-11-30.%
}

\bug{18}{fixed}
Allow |\\| in |\title|.
{\small
  Reported by Mark Senn on unknown date.
  Tested ok on 2021-11-30.%
}
