\ProvidesFile{ch-attitude-reprs.tex}[Attitude]

\chapter{Attitude}

\section{Attitude Representations}

When discussing about the orientation of a rigid body in three dimensions, otherwise known as its attitude, that orientation is implicitly understood to be relative to some other reference frame. The orientation of a book might be expressed using a frame fixed in the table it sits on. If the same book was floating in an empty void with no points of reference, there would be no reference to orient it relative to. Orientation itself is a three-dimensional quantity. Consider two reference frames: one fixed in a rigid object and a second external frame. The frame fixed in the object is known as the body frame, the second frame is known as the world frame. Any effective attitude representation must let express the directions of all three body axes in terms of the world frame basis vectors to fully define relative orientation. This raises an important question: how many numbers are needed to express an object's attitude? The direction of a unit vector can be expressed with two numbers ---  the azimuth and elevation of that vector. Naïvely, this could be extrapolated to conclude that six numbers are needed to express an orientation. Because the basis vectors form an orthonormal set $\left\{ \hat{b}_1, \hat{b}_2, \hat{b}_3\right\}$, it follows for a right-handed system that $\hat{b}_3 = \hat{b}_1 \times \hat{b}_2$, $\hat{b}_2 = \hat{b}_3 \times \hat{b}_1$, and $\hat{b}_1 = \hat{b}_2 \times \hat{b}_3$. Each of these equations constrains one further degree of freedom, revealing that a minimum of three quantities are necessary to express the relative orientation of two reference frames. This minimum bound does not make any statements about the usefulness of three element sets; at least four dimensions are needed to remove singularities. 

\subsection{The Direction Cosine Matrix}

The most obvious parameterization for attitude is the direction cosine matrix (DCM), a $3\times3$ symmetric matrix with determinant 1. The DCM is notated with two capital letters, the rightmost indicating the reference frame of the input vectors and the leftmost indicating the transformed frame. Alternatively, the DCM is sometimes expressed as $C$ when the frames involved are arbitrary or do not need to be denoted. For example, the DCM $\dcm{bn}$ takes vectors in the $\rf{n}$ frame to the $\rf{b}$ frame:

\begin{equation}
    \vrf{b}{r} = \dcm{bn} \vrf{n}{r}
\end{equation}

The orthogonal property of the DCM implies $\dcm{bn}^{-1} = \dcm{bn}^T$ such that $\dcm{bn}^T = \dcm{nb}$. 

\subsection{Principal Rotation Parameters}

Another core attitude representation is the Euler angle-axis set, otherwise known as principal rotation parameters. Euler's rotation theorem guarantees that any relative orientation can be expressed as a single rotation about an axis $\hat{\lambda} \in \mathbb{S}^2$ by an angle $\theta \in [0, 2\pi]$ \cite{crassidis1ed}. The set $\left\{\hat{\lambda},\theta\right\}$ is known as a principal rotation parameter, abbreviated PRP hereafter. The DCM is mapped to the PRP representation via \ref{eq:dcm_to_prp} \cite{shuster1993}.

\begin{align*} \numberthis \labelAndRemember{eq:dcm_to_prp}
    {
    \theta &= \cos^{-1}\left(\frac{1}{2} \left[C_{1,1} + C_{2,2} + C_{3,3} - 1 \right] \right) \\
    \hat{\lambda} &= \frac{1}{2\sin{\theta}} 
    \begin{bmatrix} C_{2,3} - C_{3,2} \\ C_{3,1}-C_{1,3} \\ C_{1,2} - C_{2,1}\end{bmatrix}
    }
\end{align*}

Where $C_{i,j}$ refers to the $i$th row and $j$th column of $C$. The mapping from PRP to DCM is also relatively straightforward.

\begin{equation} \labelAndRemember{eq:prp2dcm}
    {C = I_3 + \sin\theta\matcp{\hat{\lambda}} + (1-\cos\theta)\matcp{\hat{\lambda}}^2}
\end{equation}

Where $\matcp{v}$ is the matrix cross product operator, defined on $\vctr{v} \in \mathbb{R}^3$ as:

\begin{equation}
    \matcp{\vctr{v}} = \begin{bmatrix}
        0 & -v_3 & v_2 \\
        v_3 & 0 & -v_1 \\
        -v_2 & v_1 & 0
    \end{bmatrix}.
\end{equation}

This operator is useful as it rephrases the cross product as matrix multiplication, i.e. $\vctr{v} \times \vctr{u} = \matcp{\vctr{v}}\vctr{u}$. While the PRP $\{\theta, \hat{\lambda}\}$ is a four element set, there are only three degrees of freedom due to the unit norm constraint on $\hat{\lambda}$. 

\subsection{Quaternions}

The quaternion represents attitude with a point on the surface of the hypersphere \sthree. In terms of the PRP, the quaternion is given by Eq \ref{eq:prp2quat}.

\begin{equation} \labelAndRemember{eq:prp2quat}
    {
    \vctr{q} = \begin{bmatrix} \hat{\lambda} \sin\left( \theta \right) \\ \cos(\theta) \end{bmatrix}
    }
\end{equation}

The first three entries of the quaternion are often called the vector component, with the final entry being the scalar component. Some authors reorder the quaternion, placing the scalar term first. Often the entries of a single quaternion are referenced by index such that $\vctr{q} = \left[ q_1, q_2, q_3, q_4 \right]$. Similarly, the vector portion of the quaterion is referenced with $\vctr{q}_{1:3}$. The quaternion can be mapped back to the PRP via Eqs \ref{eq:quat2prp_theta}.

\begin{align*} \numberthis \labelAndRemember{eq:quat2prp_theta} 
    {
    \theta &= \cos^{-1}\left(q_4 \right) \\
    \lambda &= \frac{\vctr{q}_{1:3}}{\sin{\theta}}
    }
\end{align*}

The quaternion maps to the DCM via Eq \ref{eq:quat2dcm}

\begin{equation} \labelAndRemember{eq:quat2dcm}
    {
        C = \left[\begin{matrix}\ -\ q_2^2-\ q_3^2+q_1^2+q_4^2\ &\ 2\ q_1q_2+2\ q_3q_4&\ 2\ q_1q_3-2\ q_2q_4\\\ 2\ q_1q_2-2\ q_3q_4&\ -\ q_1^2-\ q_3^2+q_2^2+q_4^2\ &\ 2\ q_1q_4+2\ q_2q_3\\\ 2\ q_1q_3+2\ q_2q_4&\ 2\ q_2q_3-2\ q_1q_4&\ -q_1^2-\ q_2^2+q_3^2+q_4^2\\\end{matrix}\right]=\Xi\left(q\right)^T\Psi\left(q\right)
    }
\end{equation}

In Eq \ref{eq:quat2dcm}, $\Psi$ is defined to be \cite{crassidis1ed}

\begin{equation} \label{eq:quat_psi}
    \Psi = \left[\begin{matrix}q_4&q_3&-q_2\\{-q}_3&q_4&q_1\\q_2&-q_1&q_4\\-q_1&-q_2&-q_3\\\end{matrix}\right].
\end{equation}

\subsection{The Rotation Vector}

Multiplying the Euler angle by the axis yields an attitude representation similar to the PRP known as the rotation vector (RV), generally denoted $\vctr{p}$. 

\begin{equation} \labelAndRemember{eq:prp2rv}
    {\vctr{p} = \theta\hat{\lambda}}
\end{equation}

The RV is the first truly three dimensional representation presented so far. This is advantageous for visualizing sets of orientations, but there are multiple notable issues with any three dimensional embedding of $SO(3)$. Any representation embedded in \rthree loses some of the spherical qualities of \sthree, leading to singularities ---  regions where attitudes are not uniquely defined or are impossible to compute in the first place.

\section{Quaternion Attitude Kinematics}

Because it is cheap to convert between attitude representations, only one set of kinematic equations are needed for propagating a rigid body attitude profile from an initial condition. Quaternion kinematic differential equations are chosen as they have no singularity and produce very smooth dynamics that are easy to integrate when compared to three-variable representations that possess singularities. Given the current orientation quaternion $\vctr{q} = [q_1, q_2, q_3, q_4]^T$ and angular velocity $\vctr{\omega} = [\omega_1, \omega_2, \omega_3]^T$ the quaternion derivative is computed via Eq \ref{eq:quat_kde}

\begin{equation} \label{eq:quat_kde}
    \left[\begin{matrix}\dot{\epsilon_1}\\\dot{\epsilon_2}\\\dot{\epsilon_3}\\\dot{\epsilon_4}\\\end{matrix}\right]
    =
    \frac{1}{2}\left[\begin{matrix}\epsilon_4&-\epsilon_3&\epsilon_2&\epsilon_1\\\epsilon_3&\epsilon_4&-\epsilon_1&\epsilon_2\\-\epsilon_2&\epsilon_1&\epsilon_4&\epsilon_3\\-\epsilon_1&-\epsilon_2&-\epsilon_3&\epsilon_4\\\end{matrix}\right]
    \left[\begin{matrix}\omega_1\\\omega_2\\\omega_3\\0\\\end{matrix}\right].
\end{equation} 

\section{Quaternion Attitude Dynamics}

Rigid body dynamics can be easily expressed in the body principal axes with an arbitrary torque $\vctr{M} = \left[M_1, M_2, M_3\right]^T$ in the same frame via Eq \ref{eq:rbtf_dynamics}

\begin{equation} \label{eq:rbtf_dynamics}
    \left[\begin{matrix}\dot{\omega_1}\\\dot{\omega_2}\\\dot{\omega_3}\\\end{matrix}\right]
    =
    \left[\begin{matrix}
        \left(M_1+I_2\omega_2\omega_3-I_3\omega_2\omega_3\right) / I_1 \\
        \left(M_2-I_1\omega_1\omega_3+I_3\omega_1\omega_3\right) / I_2 \\
        \left(M_3+I_1\omega_1\omega_2-I_2\omega_1\omega_2\right) / I_3 \\
    \end{matrix}\right]
\end{equation}

\subsection{Analytic Attitude Propagation}

TODO: single axis solution, axisymmetric solution